---
title       : Regression model
subtitle    : Course project    
author      : Ilya Solopov
job         : Home
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Problem
There are following two questions:
    1. Is an automatic or manual transmission better for MPG
    2. Quantify the MPG difference between automatic and manual transmissions  
First, load the mtcars data and see at the pairwise between all variables .
```{r, echo=FALSE}
data(mtcars)
pairs(mtcars)
```

--- .class #id 

## Is automatic or manual transmission better?  
We plot a boxplot of MPG by transmission types (see appendix for plots).
```{r,echo=FALSE}
boxplot(mpg~am, data = mtcars,
        xlab = "Transmission",
        ylab = "Miles per Gallon",
        main = "MPG by Transmission Type",
        names = c("Automatic", "Manual"))
```


--- .class #id 

## t-test  
It seems that manual transmission is better in MPG than automatic.
We then perform a t-test to confirm this hypothesis
```{r,echo=FALSE}
t.test(mtcars$mpg~mtcars$am,conf.level=0.95)
```


--- .class #id 

## Quantify the difference between transmissions types  
We do linear regression between mpg and am:
```{r, echo=FALSE}
reg = lm(data = mtcars, mpg ~ am)
summary(reg)
```

--- .class #id 

## Find another factors    
We use automatic model-choosing function to find additional factors
```{r, echo=FALSE}
bestmodel = step(lm(data = mtcars, mpg ~ .), trace=0)
summary(bestmodel)
```


